### 2023-11-30 paper/main.tex
complete introduction

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
\addbibresource{main.bib}

%%%%%% Document Setup %%%%%%

\title{6.4132/16.413 Principles of Autonomy and Decision Making Final Project}
\author[ ]{Toya Takahashi}
\affil[ ]{Massachusetts Institute of Technology}
\affil[ ]{Department of Aeronautics and Astronautics}
\onehalfspacing

\begin{document}

\maketitle

\section{Introduction}

Activity planing, motion planning, and trajectory optimization for a robotic arm is challenging. To navigate around an environment, the agent must perform a state space search to plan a sequence of actions and generate a trajectory by either using a sample based planner (e.g. PRM, RRT, RRT*) or modeling the problem as a constraint optimization problem. This paper explores 1) defining an activity planning problem with the Planning Domain Definition Language (PDDL), 2) implementing the Fast-Forward (FF) heuristic planner with Enforced Hill Climbing to solve this activity planning problem, 3) using RRT with goal-biasing to generate the trajectory for the robotic arm, and 4) comparing the results with the trajectory generated from constraint optimization. The kitchen simulation environment used in this paper provides an excellent sandbox for testing and demonstrating the effectiveness of the proposed approach, in addition to learning the benefits and drawbacks of the implemented algorithms.

\section{Activity Planning}

\section{Motion Planning}

\section{Trajectory Optimization}

%%% TODO: EDIT REFERENCES %%%
\cite{Cui1}

\section{Conclusion}

\printbibliography

\end{document}

### 2023-11-30 test_example.py

@@ -92,6 +92,8 @@ def main():
 
     """ THIRD CHUNK OF CODE: MOVING THE ROBOT ARM """
 
+    # TODO: HOW TO CHECK FOR COLLISION WITHOUT "ACTUALLY" MOVING THE ARM?
+
 #    print("Going to use IK to go from a sample start state to a goal state\n")
 #    for i in range(2):
 #        print('Iteration:', i)
@@ -133,9 +135,10 @@ def main():
     world.open_drawer()
 
 
+
     """ FIFTH CHUNK OF CODE: TRANSLATING THE ENTIRE ROBOT """
 
-    print("Going to operate the base without collision checking")
+    print("Going to operate the base WITH collision checking")
     i = 0
     while True:
         goal_pos = translate_linearly(world, 0.01)
@@ -143,6 +146,8 @@ def main():
         time.sleep(TRANSLATE_SLEEP) # Add for visual purposes
         if (i % 30 == 0):
             wait_for_user()
+        if pairwise_collision(world.robot, world.kitchen):
+            break
         i += 1
     wait_for_user()
     world.destroy()

### 2023-11-30 ff_planner.py
activity planning code complete

@@ -1,0 +1,156 @@
+from pddl_parser.PDDL import PDDL_Parser
+
+class Planner:
+
+    # -----------------------------------------------
+    # Solve FF
+    # -----------------------------------------------
+
+    def calculate_hff(self, state, goal, ground_actions):
+        hff = 0
+        new_state = state
+        while not goal.issubset(state):
+            for act in ground_actions:
+                if act.positive_preconditions.issubset(state):
+                    new_state = new_state.union(act.add_effects) # Just compute the union, since no delete effects are considered
+            state = new_state
+            hff += 1
+        return hff
+
+    def solve_ff(self, domain, problem):
+
+        # Parser
+        parser = PDDL_Parser()
+        parser.parse_domain(domain)
+        parser.parse_problem(problem)
+
+        # Parsed data
+        state = parser.state
+        goal = parser.positive_goals
+
+        # Do nothing if already solved
+        if goal.issubset(state): return []
+
+        # Grounding process (enumerating all possible actions in the problem)
+        ground_actions = []
+        for action in parser.actions:
+            for act in action.groundify(parser.objects, parser.types):
+                ground_actions.append(act)
+        
+        # Search
+        plan = []
+        while not goal.issubset(state):
+
+            curr_hff = self.calculate_hff(state, goal, ground_actions)
+
+            # Greedy search
+            found_better = False
+            for act in ground_actions:
+                if act.positive_preconditions.issubset(state):
+                    new_state = self.apply(state, act.add_effects, act.del_effects)
+                    if self.calculate_hff(new_state, goal, ground_actions) < curr_hff:
+                        state = new_state
+                        plan.append(act)
+                        found_better = True
+                        break
+            if found_better: continue
+
+            # If the code reaches here, it means there is a plateau -> use BFS to continue
+            visited = set([state])
+            queue = [(state, [])]
+            found_better = False
+            while queue and not found_better:
+                q_state, q_plan = queue.pop(0)
+                for act in ground_actions:
+                    if act.positive_preconditions.issubset(q_state):
+                        new_state = self.apply(q_state, act.add_effects, act.del_effects)
+                        if new_state not in visited:
+                            if self.calculate_hff(new_state, goal, ground_actions) < curr_hff:
+                                plan.extend(q_plan + [act])
+                                state = new_state
+                                found_better = True
+                                break
+                            visited.add(new_state)
[…]

### 2023-12-01 paper/main.tex
activity planning code complete
finished activity planning yayayay

@@
 \usepackage{lineno}
+\usepackage{tikz-cd}
 \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
@@
 
+%%%%%% Main Text %%%%%%
+
 \begin{document}
@@
 Activity planing, motion planning, and trajectory optimization for a robotic arm is challenging.
-To navigate around an environment, the agent must perform a state space search to plan a sequence of actions and generate a trajectory by either using a sample based planner (e.g.
-PRM, RRT, RRT*) or modeling the problem as a constraint optimization problem.
-This paper explores 1) defining an activity planning problem with the Planning Domain Definition Language (PDDL), 2) implementing the Fast-Forward (FF) heuristic planner with Enforced Hill Climbing to solve this activity planning problem, 3) using RRT with goal-biasing to generate the trajectory for the robotic arm, and 4) comparing the results with the trajectory generated from constraint optimization.
-The kitchen simulation environment used in this paper provides an excellent sandbox for testing and demonstrating the effectiveness of the proposed approach, in addition to learning the benefits and drawbacks of the implemented algorithms.
+To navigate around an environment, the agent must perform a state space search to plan a sequence of actions and generate a trajectory by either using a sample based planner or modeling the problem as a constraint optimization problem.
+This project explores 1) defining an activity planning problem with the Planning Domain Definition Language, 2) implementing the Fast-Forward heuristic planner with Enforced Hill Climbing, 3) using RRT with goal-biasing for trajectory generation, and 4) comparing the results with the trajectory generated by constraint optimization.
+The kitchen simulation environment provides an excellent sandbox for testing and demonstrating the effectiveness of the proposed approach, in addition to learning the benefits and drawbacks of the implemented algorithms.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=190px]{sim_env.jpg}
+    \caption{The kitchen simulation environment.}
+    \label{fig:sim_env}
+\end{figure}
 
 \section{Activity Planning}
+
+\iffalse
+\subsection{Problem Statement}
+
+The simulator consists of a kitchen environment with drawers, cabinets, countertops, and a robot manipulator arm.
+In addition, sugar and spam boxes are placed on a stovetop burner and a countertop.
+The objective is to move the sugar box to a nearby countertop and store the spam box inside the red drawer below it.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=200px]{sim_env.jpg}
+    \caption{The kitchen simulation environment.}
+    \label{fig:sim_env}
+\end{figure}
+\fi
+
+\subsection{PDDL Domain and Problem}
+
+The PDDL domain and problem files encode the problem as sets of objects, types, predicates, actions, and goals.
+There are two main types of objects: the \texttt{box} type and the \texttt{storage} type.
+The \texttt{box} type represents the sugar and spam boxes which are manipulated by the robot arm, and the \texttt{storage} type represents the storage spaces in the kitchen.
+In addition, I separated the \texttt{storage} type into two subtypes: \texttt{static}, which are storage spaces without actions (stovetop burner and countertop), and \texttt{openable}, which are storage spaces that can be opened or closed (drawer, cabinet).
+
+The following assumptions were made when designing the actions and the initial state:
+\begin{itemize}
+    \item The robot can only grab one box at a time
+    \item The robot cannot open drawers or cabinets when gripping an object
+    \item Only one box can be placed on each storage space at a time
+    \item Drawers and cabinets must be open when placing or picking up a box inside them
+    \item Drawers and cabinets must be closed at both the beginning and end of the plan 
+\end{itemize}
+
+\begin{figure}[h]
+    % https://q.uiver.app/#q=WzAsNSxbMSwwLCJcXHRleHR7b2JqZWN0fSJdLFswLDMsIlxcdGV4dHtzdG9yYWdlfSJdLFsyLDMsIlxcdGV4dHtib3h9Il0sWzAsNiwiXFx0ZXh0e3N0YXRpY30iXSxbMSw2LCJcXHRleHR7b3BlbmFibGV9Il0sWzEsMCwiXFx0ZXh0e2V4dGVuZHN9Il0sWzIsMCwiXFx0ZXh0e2V4dGVuZHN9IiwyXSxbNCwxLCJcXHRleHR7ZXh0ZW5kc30iLDJdLFszLDEsIlxcdGV4dHtleHRlbmRzfSJdXQ==
+    \[\begin{tikzcd}
+        & {\text{object}} \\
+        \\
+        \\
+        {\text{storage}} && {\text{box}} \\
+        \\
+        \\
+        {\text{static}} & {\text{openable}}
+        \arrow["{\text{extends}}", from=4-1, to=1-2]
+        \arrow["{\text{extends}}"', from=4-3, to=1-2]
+        \arrow["{\text{extends}}"', from=7-2, to=4-1]
+        \arrow["{\text{extends}}", from=7-1, to=4-1]
+    \end{tikzcd}\]
+
+    \caption{Hierarchical PDDL object types including static/openable storage spaces and boxes}
+    \label{fig:types}
+\end{figure}
+
+Separating the \texttt{storage} type into subtypes allowed separating the action of placing (and picking up) a box on a storage space into \texttt{place\_static} and \texttt{place\_openable}, which has an extra \texttt{(open ?s)} precondition.
+
+I also did not use any negative preconditions to simplify the implementation of the fast-forward heuristic planner.
+For actions requiring negative preconditions, I defined a second predicate which is always the negation of the predicate needing to express the negative precondition on (e.g.
+\texttt{(open ?s - openable)} and \texttt{(closed ?s - openable)}).
+
+\subsection{Fast-Forward Heuristic Planner}
+
+The \texttt{ff\_planner} file contains all functions to solve the activity planning problem.
+The \texttt{calculate\_hff} function computes the fast-forward heuristic $h_{ff}$ of a given state by counting the number of actions (without delete effects) it takes until the goal condition is a subset of \texttt{state}.
+At each iteration, \texttt{new\_state} is computed by taking the union of the current state and the add effects of all applicable actions.
+Because we defined our actions to only have positive preconditions, we can easily determine whether an action is applicable by checking if the precondition is a subset of \texttt{new\_state}.
+$h_{ff}$ is an admissible heuristic that always underestimates the number of actions it takes to reach the goal state, hence an alternative algorithm such as A* could have been used to find the optimal path.
+
+In this project, I decided to implement Enforced Hill Climbing in the \texttt{solve\_ff} function.
+While EHC is not guaranteed to find the optimal solution, its greedy nature typically leads to higher efficiency and lower memory usage.
+\texttt{solve\_ff} initially parses the PDDL files and enumerates all possible actions that can be taken by the agent.
+Next, it performs a greedy search by immediately adding an action that leads to a strictly smaller $h_{ff}$ to the plan.
+If no such action is found, there is a ``plateau" in the graph, and BFS is used to find a sequence of actions that lead to a smaller $h_{ff}$.
+If BFS fails to find such action, then the algorithm determines that the activity planning problem is unsolvable.
+
+Comparing the performance of BFS and FF Heuristic Planner, on the contrary to my expectation, I found that BFS consistently runs faster ($650\mu s$ vs.
+$950\mu s$).
+This is most likely because the plan graph is rather simple for this problem.
+For example, the starting state has $h_{ff}=2$, meaning EHC gets stuck on a ``plateau" for most of the time, resorting to BFS.
+In this case, calculating $h_{ff}$ leads to extra computation time.
+For more complex problems requiring many actions to be taken, I expect the FF Heuristic Planner to perform significantly faster than BFS.
 

### 2023-12-01 ff_planner.py

@@ -3,17 +3,16 @@ from pddl_parser.PDDL import PDDL_Parser
 class Planner:
 
     # -----------------------------------------------
-    # Solve FF
+    # Solve FF (CUSTOM PLANNER)
     # -----------------------------------------------
 
     def calculate_hff(self, state, goal, ground_actions):
         hff = 0
         new_state = state
-        while not goal.issubset(state):
+        while not goal.issubset(new_state):
             for act in ground_actions:
-                if act.positive_preconditions.issubset(state):
+                if act.positive_preconditions.issubset(new_state):
                     new_state = new_state.union(act.add_effects) # Just compute the union, since no delete effects are considered
-            state = new_state
             hff += 1
         return hff
 
@@ -40,7 +39,6 @@ class Planner:
         # Search
         plan = []
         while not goal.issubset(state):
-
             curr_hff = self.calculate_hff(state, goal, ground_actions)
 
             # Greedy search
@@ -79,7 +77,7 @@ class Planner:
         return plan
 
     # -----------------------------------------------
-    # Solve BFS
+    # Solve BFS (EXAMPLE PLANNER)
     # -----------------------------------------------
 
     def solve_bfs(self, domain, problem):
@@ -146,6 +144,7 @@ if __name__ == '__main__':
     verbose = True
     planner = Planner()
     plan = planner.solve_ff(domain, problem)
+    #plan = planner.solve_bfs(domain, problem)
     print('Time: ' + str(time.time() - start_time) + 's')
     if type(plan) is list:
         print('plan:')

### 2023-12-02 constants.py
gathered 'hard-coded' joint values

@@ -1,0 +1,15 @@
+import numpy as np
+
+SUGAR_BOX_POSE = (-0.15, 0.65, np.pi / 4) # Starting position of sugar box
+SPAM_BOX_POSE  = (0.2, 1.1, np.pi / 4)    # Starting position of spam box
+MOVE_SLEEP     = 0.03                     # Sleep time for translation (for animation purposes)
+POS_STEP_SIZE  = 0.01                     # Step size of robot arm interpolation and RRT
+
+GRAB_SUGAR_JOINT    = (-0.07, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
+PLACE_SUGAR_JOINT   = (-np.pi / 5, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
+GRAB_SPAM_JOINT     = (-np.pi / 5 + 0.05, 7 * np.pi / 40, 0, -12 * np.pi / 20, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
+DRAWER_CLOSED_JOINT = (-7 * np.pi / 10 + 0.05, 3 * np.pi / 5, 5 * np.pi / 12 + 0.05, -3 * np.pi / 5, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
+DRAWER_OPEN_JOINT   = (-np.pi + 0.2, 3 * np.pi / 5, np.pi / 3, -3 * np.pi / 4 + 0.1, -3 * np.pi / 4, 7 * np.pi / 8, np.pi)
+STORE_SPAM_JOINT    = (-7 * np.pi / 8 + 0.2, 3 * np.pi / 8, np.pi / 2, -3 * np.pi / 4, -np.pi / 4, 7 * np.pi / 8, np.pi)
+
+

### 2023-12-02 plan_executor.py

@@ -24,17 +24,10 @@ from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, \
 
 """ CONSTANT DECLARATION """
 
-SUGAR_BOX_POSE = (-0.15, 0.65, np.pi / 4) # Starting position of sugar box
-SPAM_BOX_POSE  = (0.2, 1.1, np.pi / 4)    # Starting position of spam box
-MOVE_SLEEP     = 0.03                     # Sleep time for translation (for animation purposes)
-POS_STEP_SIZE  = 0.01                     # Step size of robot arm interpolation and RRT
-
-GRAB_SUGAR_JOINT    = (-0.07, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
-PLACE_SUGAR_JOINT   = (-np.pi / 5, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
-GRAB_SPAM_JOINT     = (-np.pi / 5 + 0.05, 7 * np.pi / 40, 0, -12 * np.pi / 20, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
-DRAWER_CLOSED_JOINT = (-7 * np.pi / 10 + 0.05, 3 * np.pi / 5, 5 * np.pi / 12 + 0.05, -3 * np.pi / 5, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
-DRAWER_OPEN_JOINT   = (-np.pi + 0.2, 3 * np.pi / 5, np.pi / 3, -3 * np.pi / 4 + 0.1, -3 * np.pi / 4, 7 * np.pi / 8, np.pi)
-STORE_SPAM_JOINT    = (-7 * np.pi / 8 + 0.2, 3 * np.pi / 8, np.pi / 2, -3 * np.pi / 4, -np.pi / 4, 7 * np.pi / 8, np.pi)
+SUGAR_BOX_POSE  = (-0.2, 0.65, np.pi / 4) # Starting position of sugar box
+SPAM_BOX_POSE   = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
+MOVE_SLEEP      = 0.03                    # Sleep time for translation (for animation purposes)
+POS_STEP_SIZE   = 0.01                    # Step size of robot arm interpolation and RRT
 
 add_sugar_box = lambda world, **kwargs: add_ycb(world, 'sugar_box', **kwargs)
[…]

### 2023-12-02 rrt.py

@@ -1,0 +1,93 @@
+import math
+
+from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name
+from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, interval_generator, get_link_pose, interpolate_poses
+
+from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO, FRANKA_URDF
+from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinematics
+from src.world import World
+from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, \
+    ALL_JOINTS, compute_surface_aabb, get_sample_fn, \
+    BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, \
+    STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, \
+
+
+from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, interval_generator, get_link_pose, interpolate_poses
+
+GOAL_SAMPLE = 2
+POS_STEP_SIZE = 0.01
+
+class Tree:
+    def __init__(self, point):
+        self.parent = None
+        self.children = []
+        self.point = point
+    
+    def add_child(self, child):
+        self.children.append(child)
+        child.parent = self
+    
+    def set_parent(self, parent):
+        parent.add_child(self)
+        
+    @property
+    def size(self):
+        if len(self.children) == 0: return 1
+        return sum([child.size for child in self.children]) + 1
+
+class TrajectoryGenerator:
+
+    def __init__(self, world):
+        self.world = world
+        self.tool_link = link_from_name(world.robot, 'panda_hand')
+        self.sample_free = get_sample_fn(world.robot, world.arm_joints)
+
+    def rrt(self, goal_pose):
+        start_pose = get_link_pose(self.world.robot, self.tool_link)
+        tree = Tree(start_pose)
+        count = 1
+        while True:
[…]

### 2023-12-02 src/utils.py

@@ -11,13 +11,14 @@ from collections import namedtuple
 
 from pybullet_tools.pr2_primitives import Conf
 from pybullet_tools.pr2_utils import get_top_grasps, get_side_grasps, close_until_collision
-from pybullet_tools.utils import joints_from_names, joint_from_name, Attachment, link_from_name, get_unit_vector, \
-    unit_pose, BodySaver, multiply, Pose, \
+from pybullet_tools.utils import joint_from_name, Attachment, link_from_name, get_unit_vector, \
+    unit_pose, BodySaver, multiply, Pose, Point, stable_z_on_aabb, \
     get_link_subtree, clone_body, get_all_links, invert, get_link_pose, set_pose, interpolate_poses, set_color, LockRenderer, get_body_name, randomize, unit_point, create_obj, BASE_LINK, get_link_descendants, \
     get_aabb, get_collision_data, point_from_pose, get_data_pose, get_data_extents, AABB, \
     apply_affine, get_aabb_vertices, aabb_from_points, read_obj, tform_mesh, create_attachment, draw_point, \
     child_link_from_joint, is_placed_on_aabb, pairwise_collision, flatten_links, has_link, get_difference_fn, Euler, approximate_as_prism, \
     get_joint_positions, implies, unit_from_theta
+from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, interval_generator, get_link_pose, interpolate_poses
 
 MODELS_PATH = os.path.join(os.path.dirname(os.path.abspath(__file__)), os.pardir, 'models/')
 
@@ -208,6 +209,25 @@ def add_ycb(world, ycb_type, idx=0, counter=0, **kwargs):
     world.add_body(name, color=np.ones(4))
     pose2d_on_surface(world, name, COUNTERS[counter], **kwargs)
     return name
+
+def pose2d_on_surface(world, entity_name, surface_name, pose2d=(0., 0., 0.)):
+    x, y, yaw = pose2d
+    body = world.get_body(entity_name)
+    surface_aabb = compute_surface_aabb(world, surface_name)
+    z = stable_z_on_aabb(body, surface_aabb)
+    pose = Pose(Point(x, y, z), Euler(yaw=yaw))
+    set_pose(body, pose)
+    return pose
+
+add_sugar_box = lambda world, **kwargs: add_ycb(world, 'sugar_box', **kwargs)
[…]

### 2023-12-03 constants.py
finished rrt code

@@ -1,15 +1,19 @@
 import numpy as np
 
-SUGAR_BOX_POSE = (-0.15, 0.65, np.pi / 4) # Starting position of sugar box
-SPAM_BOX_POSE  = (0.2, 1.1, np.pi / 4)    # Starting position of spam box
-MOVE_SLEEP     = 0.03                     # Sleep time for translation (for animation purposes)
-POS_STEP_SIZE  = 0.01                     # Step size of robot arm interpolation and RRT
+SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box
+SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)    # Starting position of spam box
+#MOVE_SLEEP       = 0.03                     # Sleep time for translation (for animation purposes)
+MOVE_SLEEP       = 0
+JOINT_MOVE_SLEEP = 0.05
+JOINT_STEP_SIZE  = 0.02                     # Step size of robot arm interpolation and RRT
+GOAL_SAMPLE      = 10                        # Sample goal every X times
+GOAL_THRESHOLD   = 0.1                      # If distance less than this, then it is in goal state
 
-GRAB_SUGAR_JOINT    = (-0.07, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
-PLACE_SUGAR_JOINT   = (-np.pi / 5, np.pi / 2, np.pi, 0, np.pi / 4, np.pi, np.pi)
-GRAB_SPAM_JOINT     = (-np.pi / 5 + 0.05, 7 * np.pi / 40, 0, -12 * np.pi / 20, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
-DRAWER_CLOSED_JOINT = (-7 * np.pi / 10 + 0.05, 3 * np.pi / 5, 5 * np.pi / 12 + 0.05, -3 * np.pi / 5, -3 * np.pi / 4, 3 * np.pi / 4, np.pi)
-DRAWER_OPEN_JOINT   = (-np.pi + 0.2, 3 * np.pi / 5, np.pi / 3, -3 * np.pi / 4 + 0.1, -3 * np.pi / 4, 7 * np.pi / 8, np.pi)
-STORE_SPAM_JOINT    = (-7 * np.pi / 8 + 0.2, 3 * np.pi / 8, np.pi / 2, -3 * np.pi / 4, -np.pi / 4, 7 * np.pi / 8, np.pi)
-
+# Hard-coded joints
[…]

### 2023-12-03 rrt.py

@@ -1,21 +1,22 @@
+import os
+import sys
 import math
 
-from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name
-from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, interval_generator, get_link_pose, interpolate_poses
+sys.setrecursionlimit(1500)
+sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
-from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO, FRANKA_URDF
-from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinematics
-from src.world import World
-from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, \
-    ALL_JOINTS, compute_surface_aabb, get_sample_fn, \
-    BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, \
-    STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, \
+from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, interval_generator, get_joint_positions, set_renderer, set_joint_positions, pairwise_collision
+from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
+from pybullet_tools.ikfast.ikfast import get_ik_joints
+from constants import *
 
-
-from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, interval_generator, get_link_pose, interpolate_poses
-
-GOAL_SAMPLE = 2
-POS_STEP_SIZE = 0.01
+def get_sample_fn(body, joints, custom_limits={}, **kwargs):
+    lower_limits, upper_limits = get_custom_limits(body, joints, custom_limits, circular_limits=CIRCULAR_LIMITS)
[…]

### 2023-12-03 src/utils.py

@@ -222,13 +222,6 @@ def pose2d_on_surface(world, entity_name, surface_name, pose2d=(0., 0., 0.)):
 add_sugar_box = lambda world, **kwargs: add_ycb(world, 'sugar_box', **kwargs)
 add_spam_box = lambda world, **kwargs: add_ycb(world, 'potted_meat_can', **kwargs)
 
-def get_sample_fn(body, joints, custom_limits={}, **kwargs):
-    lower_limits, upper_limits = get_custom_limits(body, joints, custom_limits, circular_limits=CIRCULAR_LIMITS)
-    generator = interval_generator(lower_limits, upper_limits, **kwargs)
-    def fn():
-        return tuple(next(generator))
-    return fn
-
 def ycb_type_from_file(path):
     return path.split('_', 1)[-1]
 

### 2023-12-03 ss-pybullet/pybullet_tools/utils.py

@@ -1,4 +1,4 @@
-from __future__ import print_function
+#from __future__ import print_function
 
 import colorsys
 import inspect
@@ -2589,6 +2589,7 @@ def pairwise_collision(body1, body2, **kwargs):
     if isinstance(body1, tuple) or isinstance(body2, tuple):
         body1, links1 = expand_links(body1)
         body2, links2 = expand_links(body2)
+        print(links2)
         return any_link_pair_collision(body1, links1, body2, links2, **kwargs)
     return body_collision(body1, body2, **kwargs)
 

### 2023-12-03 test_example.py

@@ -8,33 +8,15 @@ import numpy as np
 
 sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
-from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name
-from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, get_joint_positions, interval_generator, get_link_pose, interpolate_poses
+from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, single_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name, CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, get_joint_positions, interval_generator, get_link_pose, interpolate_poses, set_renderer
 
 from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO, FRANKA_URDF
 from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinematics
 
 from src.world import World
-from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, \
-    ALL_JOINTS, compute_surface_aabb, rotate_robot, \
-    BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, \
-    STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, \
-    add_ycb, get_sample_fn
-
-
-""" CONSTANT DECLARATION """
-
[…]

### 2023-12-03 constants.py
working part 2 code, just need animation

@@ -1,19 +1,19 @@
 import numpy as np
 
 SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box
-SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)    # Starting position of spam box
-#MOVE_SLEEP       = 0.03                     # Sleep time for translation (for animation purposes)
-MOVE_SLEEP       = 0
-JOINT_MOVE_SLEEP = 0.05
-JOINT_STEP_SIZE  = 0.02                     # Step size of robot arm interpolation and RRT
-GOAL_SAMPLE      = 10                        # Sample goal every X times
-GOAL_THRESHOLD   = 0.1                      # If distance less than this, then it is in goal state
+SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
+MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
+ACTION_SLEEP     = 1                       # Sleep time between actions
+JOINT_MOVE_SLEEP = 0.04
+JOINT_STEP_SIZE  = 0.02                    # Step size of robot arm interpolation and RRT
+GOAL_SAMPLE      = 15                      # Sample goal every X times
+GOAL_THRESHOLD   = 0.20                    # If distance less than this, then it is in goal state
 
 # Hard-coded joints
 GRAB_SUGAR_JOINT    = (-0.10029298683257405, 0.8075911195804472, 0.06859836909844828, -1.4332957958078696, 0.019711396650709645, 3.024185878659845, 0.6934382572596789)
 PLACE_SUGAR_JOINT   = (-0.8333839072116455, 0.8531772629931089, 0.4617390279322891, -1.381649993484035, 0.30737591885150817, 2.8317178374508676, -0.11349712635040898)
 GRAB_SPAM_JOINT     = (-0.2952415992141341, 0.7212760573498352, -0.5825837608323721, -1.9038112672075966, 2.43044497001763, 1.7815317165161315, -1.6864013281698946)
 DRAWER_CLOSED_JOINT = (-1.338462590924967, 1.0771823871221202, 0.18560027115857658, -1.5159392166440764, 1.7676538992294342, 1.87285428791979, -0.2862073274847683)
[…]

### 2023-12-03 plan_executor.py

@@ -2,171 +2,64 @@ from __future__ import print_function
 
 import os
 import sys
-import argparse
 import time
 import numpy as np
 
 sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
-from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name
-from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, get_joint_positions, interval_generator, get_link_pose, interpolate_poses
+from pybullet_tools.utils import wait_for_user, link_from_name
 
-from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO, FRANKA_URDF
-from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinematics
+from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
+from pybullet_tools.ikfast.ikfast import get_ik_joints
 
 from src.world import World
-from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, \
-    ALL_JOINTS, compute_surface_aabb, rotate_robot, \
-    BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, \
-    STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, \
-    add_ycb, get_sample_fn
-
-
-""" CONSTANT DECLARATION """
-
-SUGAR_BOX_POSE  = (-0.2, 0.65, np.pi / 4) # Starting position of sugar box
-SPAM_BOX_POSE   = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
-MOVE_SLEEP      = 0.03                    # Sleep time for translation (for animation purposes)
-POS_STEP_SIZE   = 0.01                    # Step size of robot arm interpolation and RRT
+from src.utils import add_ycb
+from robot import Robot
+from ff_planner import Planner
+from constants import *
 
[…]

### 2023-12-03 robot.py

@@ -1,0 +1,86 @@
+import time
+from pybullet_tools.utils import set_joint_positions
+from src.utils import rotate_robot, translate_linearly, add_ycb
+from constants import *
+from rrt import *
+
+class Robot:
+
+    def move_base(self, world):
+        for _ in range(45):
+            goal_pos = rotate_robot(world, -0.01)
+            set_joint_positions(world.robot, world.base_joints, goal_pos)
+            time.sleep(MOVE_SLEEP)
+        for _ in range(140):
+            goal_pos = translate_linearly(world, 0.01)
+            set_joint_positions(world.robot, world.base_joints, goal_pos)
+            time.sleep(MOVE_SLEEP)
+        for _ in range(45):
+            goal_pos = rotate_robot(world, 0.01)
+            set_joint_positions(world.robot, world.base_joints, goal_pos)
+            time.sleep(MOVE_SLEEP)
+        world.open_gripper()
+
+    def grab_sugar(self, world, ik_joints):
+        time.sleep(ACTION_SLEEP)
+        path = TrajectoryGenerator().rrt(world, GRAB_SUGAR_JOINT)
+        for point in path:
+            set_joint_positions(world.robot, ik_joints, point)
+            time.sleep(JOINT_MOVE_SLEEP)
+        world.close_gripper()
+
+    def place_sugar(self, world, ik_joints):
+        time.sleep(ACTION_SLEEP)
+        path = TrajectoryGenerator().rrt(world, PLACE_SUGAR_JOINT)
+        for point in path:
+            set_joint_positions(world.robot, ik_joints, point)
+            time.sleep(JOINT_MOVE_SLEEP)
+        world.open_gripper()
+
+    def grab_spam(self, world, ik_joints):
+        time.sleep(ACTION_SLEEP)
+        path = TrajectoryGenerator().rrt(world, GRAB_SPAM_JOINT)
+        for point in path:
+            set_joint_positions(world.robot, ik_joints, point)
+            time.sleep(JOINT_MOVE_SLEEP)
+        world.close_gripper()
+
+    def place_spam(self, world, ik_joints):
+        time.sleep(ACTION_SLEEP)
+        path = TrajectoryGenerator().rrt(world, STORE_SPAM_JOINT)
+        for point in path:
+            set_joint_positions(world.robot, ik_joints, point)
+            time.sleep(JOINT_MOVE_SLEEP)
+        world.open_gripper()
+
[…]

### 2023-12-03 rrt.py

@@ -12,7 +12,6 @@ from constants import *
 
 def get_sample_fn(body, joints, custom_limits={}, **kwargs):
     lower_limits, upper_limits = get_custom_limits(body, joints, custom_limits, circular_limits=CIRCULAR_LIMITS)
-    print("limits:", lower_limits, upper_limits)
     generator = interval_generator(lower_limits, upper_limits, **kwargs)
     def fn():
         return tuple(next(generator))
@@ -27,14 +26,6 @@ class Tree:
     def add_child(self, child):
         self.children.append(child)
         child.parent = self
-    
-    def set_parent(self, parent):
-        parent.add_child(self)
-        
-    @property
-    def size(self):
-        if len(self.children) == 0: return 1
-        return sum([child.size for child in self.children]) + 1
 
 class TrajectoryGenerator:
 

### 2023-12-03 src/world.py

@@ -354,9 +354,14 @@ class World(object):
         set_joint_position(self.kitchen, joint, self.closed_conf(joint))
     def open_door(self, joint):
         set_joint_position(self.kitchen, joint, self.open_conf(joint))
+    def close_drawer(self):
+        joint = joint_from_name(self.kitchen, "indigo_drawer_top_joint")
+        set_joint_position(self.kitchen, joint, self.closed_conf(joint))
     def open_drawer(self):
         joint = joint_from_name(self.kitchen, "indigo_drawer_top_joint")
         set_joint_position(self.kitchen, joint, self.open_conf(joint))
+
+
 
     #########################
 

### 2023-12-03 test_example.py

@@ -73,25 +73,25 @@ def main():
 
     """ THIRD CHUNK OF CODE: MOVING THE ROBOT ARM """
 
-#    wait_for_user()
-#    print("Open drawer")
-#    world.open_drawer()
-#
-#
-#    print("Going to use IK to go from a sample start state to a goal state\n")
-#    wait_for_user()
-#    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
-#    start_pose = get_link_pose(world.robot, tool_link)
-#    print("Start pose:", start_pose)
-#    end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
-#    #end_pose = (0.5, 1.2, -0.5), (0, -0.707, 0, 0.707)
-#    conf = next(closest_inverse_kinematics(world.robot, PANDA_INFO, tool_link, end_pose, max_time=0.05), None)
-#    if conf is None:
-#        print('Failure!')
-#    else:
-#        print(conf)
-#        set_joint_positions(world.robot, ik_joints, conf)
-#
+    wait_for_user()
+    print("Open drawer")
+    world.open_drawer()
+
+
+    print("Going to use IK to go from a sample start state to a goal state\n")
+    wait_for_user()
+    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
+    start_pose = get_link_pose(world.robot, tool_link)
+    print("Start pose:", start_pose)
+    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
+    end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
+    conf = next(closest_inverse_kinematics(world.robot, PANDA_INFO, tool_link, end_pose, max_time=0.05), None)
+    if conf is None:
+        print('Failure!')
+    else:
+        print(conf)
+        set_joint_positions(world.robot, ik_joints, conf)
+
 #
 #
 #    """ FOURTH CHUNK OF CODE: CHECKING DIFFERENT FUNCTIONS """

### 2023-12-03 constants.py
finished part 2 code

@@ -7,9 +7,15 @@ ACTION_SLEEP     = 1                       # Sleep time between actions
 JOINT_MOVE_SLEEP = 0.04
 JOINT_STEP_SIZE  = 0.02                    # Step size of robot arm interpolation and RRT
 GOAL_SAMPLE      = 15                      # Sample goal every X times
-GOAL_THRESHOLD   = 0.20                    # If distance less than this, then it is in goal state
+GOAL_THRESHOLD   = 0.15                    # If distance less than this, then it is in goal state
+
+# Pose of objects after being moved
+MOVED_SUGAR_POSE = (0.1, 1.0, -0.6),  (0, 0, 0, 1) 
+MOVED_SPAM_POSE  = (0.5, 1.2, -0.69), (0, 0, 0, 1) 
+STORED_SPAM_POSE = (0.2, 1.2, -0.69),  (0, 0, 0, 1) 
 
 # Hard-coded joints
+INIT_JOINT          = (0.01200158428400755, -0.5697816014289856, 5.6801487517077476e-05, -2.8105969429016113, -0.00025768374325707555, 3.0363450050354004, 0.7410701513290405)
 GRAB_SUGAR_JOINT    = (-0.10029298683257405, 0.8075911195804472, 0.06859836909844828, -1.4332957958078696, 0.019711396650709645, 3.024185878659845, 0.6934382572596789)
 PLACE_SUGAR_JOINT   = (-0.8333839072116455, 0.8531772629931089, 0.4617390279322891, -1.381649993484035, 0.30737591885150817, 2.8317178374508676, -0.11349712635040898)
 GRAB_SPAM_JOINT     = (-0.2952415992141341, 0.7212760573498352, -0.5825837608323721, -1.9038112672075966, 2.43044497001763, 1.7815317165161315, -1.6864013281698946)

### 2023-12-03 plan_executor.py

@@ -2,15 +2,10 @@ from __future__ import print_function
 
 import os
 import sys
-import time
-import numpy as np
 
 sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
-from pybullet_tools.utils import wait_for_user, link_from_name
-
-from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
-from pybullet_tools.ikfast.ikfast import get_ik_joints
+from pybullet_tools.utils import wait_for_user
 
 from src.world import World
 from src.utils import add_ycb
@@ -35,31 +30,18 @@ def main():
         return
 
     # Setup world
-    np.set_printoptions(precision=3, suppress=True)
     world = World(use_gui=True)
     add_sugar_box(world, idx=0, counter=1, pose2d=SUGAR_BOX_POSE)
     add_spam_box(world, idx=1, counter=0, pose2d=SPAM_BOX_POSE)
     world._update_initial()
-    tool_link = link_from_name(world.robot, 'panda_hand')
-    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
-
-    # Initial movement
-    robot = Robot()
-    robot.move_base(world)
-    function_map = {
-        "open_storage":     {"drawer": robot.open_drawer},
-        "close_storage":    {"drawer": robot.close_drawer},
-        "pick_up_static":   {"sugar": robot.grab_sugar,  "spam": robot.grab_spam},
-        "pick_up_openable": {"sugar": robot.grab_sugar,  "spam": robot.grab_spam},
-        "place_openable":   {"sugar": robot.place_sugar, "spam": robot.place_spam},
-        "place_static":     {"sugar": robot.place_sugar, "spam": robot.place_spam},
-    }
 
     # Execute plan
+    robot = Robot(world)
+    robot.move_base()
     for act in plan:
-        act_name  = act.name
-        act_param = act.parameters[0]
-        function_map[act_name][act_param](world, ik_joints)
+        print(act)
+        robot.act(act.name, act.parameters[0])
+    robot.move_joint_init()
 
     wait_for_user()
     world.destroy()

### 2023-12-03 robot.py

@@ -1,86 +1,120 @@
 import time
-from pybullet_tools.utils import set_joint_positions
-from src.utils import rotate_robot, translate_linearly, add_ycb
+from pybullet_tools.utils import set_joint_positions, set_pose, get_link_pose
+from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
+from src.utils import rotate_robot, translate_linearly
 from constants import *
 from rrt import *
 
 class Robot:
 
-    def move_base(self, world):
+    def __init__(self, world):
+        self.world = world
+        self.tool_link = link_from_name(world.robot, "panda_hand")
+        self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
+        self.sugar_box = self.world.get_body("sugar_box0")
+        self.spam_box = self.world.get_body("potted_meat_can1")
+
+        self.function_map = {
+            "open_storage":     {"drawer": self.open_drawer},
+            "close_storage":    {"drawer": self.close_drawer},
+            "pick_up_static":   {"sugar":  self.grab_sugar,  "spam": self.grab_spam},
+            "pick_up_openable": {"sugar":  self.grab_sugar,  "spam": self.grab_spam},
+            "place_openable":   {"sugar":  self.place_sugar, "spam": self.place_spam},
+            "place_static":     {"sugar":  self.place_sugar, "spam": self.place_spam},
+        }
+
+    def move_base(self):
         for _ in range(45):
-            goal_pos = rotate_robot(world, -0.01)
-            set_joint_positions(world.robot, world.base_joints, goal_pos)
+            goal_pos = rotate_robot(self.world, -0.01)
+            set_joint_positions(self.world.robot, self.world.base_joints, goal_pos)
             time.sleep(MOVE_SLEEP)
         for _ in range(140):
-            goal_pos = translate_linearly(world, 0.01)
-            set_joint_positions(world.robot, world.base_joints, goal_pos)
+            goal_pos = translate_linearly(self.world, 0.01)
+            set_joint_positions(self.world.robot, self.world.base_joints, goal_pos)
             time.sleep(MOVE_SLEEP)
         for _ in range(45):
-            goal_pos = rotate_robot(world, 0.01)
-            set_joint_positions(world.robot, world.base_joints, goal_pos)
[…]

### 2023-12-03 test_example.py

@@ -72,25 +72,30 @@ def main():
         time.sleep(MOVE_SLEEP)
 
     """ THIRD CHUNK OF CODE: MOVING THE ROBOT ARM """
-
-    wait_for_user()
+#
+#    wait_for_user()
     print("Open drawer")
     world.open_drawer()
+#
 
-
-    print("Going to use IK to go from a sample start state to a goal state\n")
-    wait_for_user()
+#    print("Going to use IK to go from a sample start state to a goal state\n")
+#    wait_for_user()
     ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
     start_pose = get_link_pose(world.robot, tool_link)
-    print("Start pose:", start_pose)
-    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
-    end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
-    conf = next(closest_inverse_kinematics(world.robot, PANDA_INFO, tool_link, end_pose, max_time=0.05), None)
-    if conf is None:
-        print('Failure!')
-    else:
-        print(conf)
-        set_joint_positions(world.robot, ik_joints, conf)
+#    print("Start pose:", start_pose)
+#    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
+#    end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
+#    conf = next(closest_inverse_kinematics(world.robot, PANDA_INFO, tool_link, end_pose, max_time=0.05), None)
+#    if conf is None:
+#        print('Failure!')
+#    else:
+#        print(conf)
+#        set_joint_positions(world.robot, ik_joints, conf)
+
+    wait_for_user()
+    set_joint_positions(world.robot, ik_joints, STORE_SPAM_JOINT)
+    set_pose(world.get_body("potted_meat_can1"), MOVED_SPAM_POSE)
+    print("pose:", get_link_pose(world.robot, tool_link))
 
 #
 #
@@ -122,60 +127,60 @@ def main():
 #        if pairwise_collision(world.robot, world.kitchen):
 #            break
 #        i += 1
-
-    """ SIXTH CHUNK OF CODE: MOVE ARM TO OBJECTS """
-    
-    print("Grab sugar box")
-    wait_for_user()
-    traj_gen = TrajectoryGenerator()
[…]

### 2023-12-04 paper/main.tex
finished part 2

@@
 \documentclass{article}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{graphicx}
-\graphicspath{ {./figures/} }
 \usepackage{subcaption}
@@
 \usepackage{tikz-cd}
+\usepackage{hyperref}
 \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
+
+\graphicspath{ {./figures/} }
+\hypersetup{
+    colorlinks=true,
+    citecolor=black,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=blue,
+    pdftitle={Overleaf Example},
+    pdfpagemode=FullScreen,
+}
 \addbibresource{main.bib}
@@
     \includegraphics[width=190px]{sim_env.jpg}
-    \caption{The kitchen simulation environment.}
+    \caption{The kitchen simulation environment}
     \label{fig:sim_env}
@@
 
+To view the sample-based motion planner in action, see \href{https://drive.google.com/file/d/1sknWGIKYpLsJexYLzeWbSfdt8TrVTznH/view?usp=sharing}{FF Heuristic Planner and RRT Trajectory Generator} or go to the following url: \url{https://drive.google.com/file/d/1sknWGIKYpLsJexYLzeWbSfdt8TrVTznH/view?usp=drive_link}.
+
+\subsection{Environment Assumptions}
+
+Hard-coded values can be found in \texttt{constants.py} and includes:
+\begin{itemize}
+    \item The initial 2D poses of the spam and sugar boxes (were not modified significantly from the original positions, simply moved the sugar box closer for the robot arm to reach)
+    \item The 3D poses of the spam and sugar boxes after moved by the robot
+    \item The 7D goal joint position vectors for the different actions
+    \item \texttt{JOINT\_STEP\_SIZE}, \texttt{GOAL\_SAMPLE}, and \texttt{GOAL\_THRESHOLD} (explained in \href{sec:rrt}{Trajectory Generation using RRT})
+\end{itemize}
+
+In addition, the following assumptions were made when implementing the motion planner:
+\begin{itemize}
+    \item The sugar/spam box attaches to the end-effector once the ``grab" action finishes
+    \item The drawer opens after the ``open drawer" action ends and closes before the ``close drawer" action begins
+\end{itemize}
+
+Importantly, the collision detection in my RRT implementation is simplified from traditional methods.
+Typically, when checking if a newly sampled point can be reached without collisions, RRT calculates whether the line between the new point and its nearest point in the tree intersects with an obstacle.
+However, in my implementation, I only check whether the new sampled point is inside an obstacle, meaning the robot collides with an object in the kitchen environment.
+This simplification can be made because the robot bodies are large and the distance between each node in the tree are small, meaning if a new joint configuration does not cause a collision, it is almost guaranteed that all joint configurations between the new point and its closest point are valid.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=190px]{rrt_collision.jpg}
+    \caption{Collision detection in RRT}
+    \label{fig:rrt_collision}
+\end{figure}
+
+\subsection{Trajectory Generation using RRT}
+\label{sec:rrt}
+
+The sample-based motion planning algorithm is written in \texttt{rrt.py}.
+\texttt{get\_sample\_fn} returns a sampling function that returns a random valid joint configuration $x_\text{rand}$.
+I also defined a class \texttt{Tree} which keeps track of its \texttt{parent}, \texttt{children}, and value (\texttt{point}), which is the 7D joint configuration.
+\texttt{Tree} has function \texttt{add\_child}, which appends a new \texttt{Tree} to its \texttt{children} and sets the child's \texttt{parent} to itself.
+
+Class \texttt{TrajectoryGenerator} contains the main motion planning algorithm in the \texttt{rrt} method. It also includes four helper functions:
+\begin{enumerate}
+    \item \texttt{find\_nearest}: returns $x_\text{nearest}$, the node in the tree closest to $x_\text{rand}$ by recursively traversing the tree.
+    \item \texttt{steer}: creates a straight line from $x_\text{nearest}$ to $x_\text{rand}$ limited to length \texttt{JOINT\_STEP\_SIZE}. Returns this new point $x_\text{new}$.
+    \item \texttt{obstacle\_free}: returns true if the input joint configuration does not cause the robot to collide with a kitchen object.
+    \item \texttt{find\_path}: returns a list of joint configurations from the initial state to the goal state by following the parent pointers.
+\end{enumerate}
+
+RRT is then implemented as follows using the helper functions:
+\begin{algorithm}
+\caption{Rapidly-Exploring Random Tree (RRT)}\label{alg:rrt}
+\begin{algorithmic}
+\State $\mathtt{tree} \gets \mathtt{Tree()}$
+\State $i \gets 1$
+\While{\texttt{True}}
+    \If{$i\mod\mathtt{GOAL\_SAMPLE}=0$}
+        \State $x_\text{rand} \gets x_\text{goal}$
+    \Else
+        \State $x_\text{rand} \gets \mathtt{sample\_free()}$
+    \EndIf
+    \State $x_\text{nearest} \gets \mathtt{find\_nearest(tree}, x_\text{rand})$
+    \State $x_\text{new} \gets \mathtt{steer}(x_\text{nearest}, x_\text{rand})$
+    \If{$\mathtt{obstacle\_free}(x_\text{new})$}
+    \State $x_\text{last} \gets \mathtt{Tree}(x_\text{new})$
+        \State $x_\text{nearest}\mathtt{.add\_child}(x_\text{last})$
+        \If{$\mathtt{dist}(x_\text{new}, x_\text{goal})\le\mathtt{GOAL\_THRESHOLD}$}
+            \State \Return{$\mathtt{find\_path}(x_\text{last})$}
+        \EndIf 
+        \State $i \gets i + 1$
+    \EndIf 
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+
+Instead of getting a random sample every time, the algorithm uses the goal state as the ``random" value every \texttt{GOAL\_SAMPLE} cycles to bias the tree towards the goal.
+Additionally, we determine whether $x_\text{new}$ is in the goal state by checking if the euclidian distance between $x_\text{new}$ and $x_\text{goal}$ is less than \texttt{GOAL\_THRESHOLD}.
+
+While the algorithm successfully generates a trajectory as shown in the video, it can be slow depending on the initial and goal state.
+Constants needed to be tuned to increase the performance of the algorithm.
+
+\subsection{Integration with the Activity Planner}
+
+The \texttt{robot.py} file includes a \texttt{Robot} class with methods for each action in the PDDL domain.
+It also includes methods to move the robot base closer to the objects and the robot arm back to the initial state.
+Finally, the dictionary \texttt{function\_map} maps PDDL actions to its corresponding methods, and the \texttt{act} method uses this dictionary to perform a task based on the input PDDL action.
+
+The overall plan execution is written in \texttt{plan\_executor.py}.
+The code initially solves the activity planning problem using the FF Heuristic Planner, which returns a list of tasks to execute.
+\texttt{plan\_executor} simply iterates through this list and calls the \texttt{Robot().act} method for each action to fully execute the plan.
+
 \section{Trajectory Optimization}
+
+\section{Conclusion}
 
@@
 
-\section{Conclusion}
-
 \printbibliography

### 2023-12-04 constants.py

@@ -1,10 +1,13 @@
 import numpy as np
 
+# For animation purposes
+JOINT_MOVE_SLEEP = 0.04                    # Sleep time between joint movements
+ACTION_SLEEP     = 1                       # Sleep time between actions
+MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
+
+# Important constants
 SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box
 SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
-MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
-ACTION_SLEEP     = 1                       # Sleep time between actions
-JOINT_MOVE_SLEEP = 0.04
 JOINT_STEP_SIZE  = 0.02                    # Step size of robot arm interpolation and RRT
 GOAL_SAMPLE      = 15                      # Sample goal every X times
 GOAL_THRESHOLD   = 0.15                    # If distance less than this, then it is in goal state

### 2023-12-04 plan_executor.py

@@ -36,6 +36,7 @@ def main():
     world._update_initial()
 
     # Execute plan
+    wait_for_user()
     robot = Robot(world)
     robot.move_base()
     for act in plan:

### 2023-12-04 rrt.py

@@ -37,7 +37,6 @@ class TrajectoryGenerator:
 
         start_point = get_joint_positions(world.robot, world.arm_joints)
         tree = Tree(start_point)
-        nodes = [tree]
         count = 1
         while True:
             rand_point = goal_point if count % GOAL_SAMPLE == 0 else sample_free() # Goal biasing
@@ -45,7 +44,6 @@ class TrajectoryGenerator:
             new_point = self.steer(nearest.point, rand_point)
             if self.obstacle_free(world, joints, new_point):
                 last_node = Tree(new_point)
-                nodes.append(last_node)
                 nearest.add_child(last_node)
                 if math.dist(new_point, goal_point) <= GOAL_THRESHOLD: break # In goal state
             count += 1

### 2023-12-05 constants.py
initial trajopt complete

@@ -3,14 +3,16 @@ import numpy as np
 # For animation purposes
 JOINT_MOVE_SLEEP = 0.04                    # Sleep time between joint movements
 ACTION_SLEEP     = 1                       # Sleep time between actions
-MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
+#MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
+MOVE_SLEEP       = 0                    # Sleep time for translation (for animation purposes)
 
 # Important constants
 SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box
 SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
 JOINT_STEP_SIZE  = 0.02                    # Step size of robot arm interpolation and RRT
-GOAL_SAMPLE      = 15                      # Sample goal every X times
+GOAL_SAMPLE      = 50                      # Sample goal every X times
 GOAL_THRESHOLD   = 0.15                    # If distance less than this, then it is in goal state
+PATH_LENGTH  = 200                         # Path length for constraint optimization solver
 
 # Pose of objects after being moved
 MOVED_SUGAR_POSE = (0.1, 1.0, -0.6),  (0, 0, 0, 1) 

### 2023-12-05 example_drake.py

@@ -1,0 +1,47 @@
+from pydrake.solvers import MathematicalProgram, Solve
+import numpy as np
+import matplotlib.pyplot as plt
+
+prog = MathematicalProgram()
+p1 = prog.NewContinuousVariables(2, "p1")
+p2 = prog.NewContinuousVariables(2, "p2")
+
+# Add the constraint that p1 is on the unit circle centered at (0, 2)
+prog.AddConstraint(
+    lambda z: [z[0]**2 + (z[1]-2)**2],
+    lb=np.array([1.]),
+    ub=np.array([1.]),
+    vars=p1)
+
+# Add the constraint that p2 is on the curve y=x*x
+prog.AddConstraint(
+    lambda z: [z[1] - z[0]**2],
+    lb=[0.],
+    ub=[0.],
+    vars=p2)
+
+# Add the cost on the distance between p1 and p2
+prog.AddQuadraticCost((p1-p2).dot(p1-p2))
+
+# Set the value of p1 in initial guess to be [0, 1]
+prog.SetInitialGuess(p1, [0., 1.])
+# Set the value of p2 in initial guess to be [1, 1]
+prog.SetInitialGuess(p2, [1., 1.])
+
+# Now solve the program
+result = Solve(prog)
+print(f"Is optimization successful? {result.is_success()}")
+p1_sol = result.GetSolution(p1)
+p2_sol = result.GetSolution(p2)
+print(f"solution to p1 {p1_sol}")
+print(f"solution to p2 {p2_sol}")
+print(f"optimal cost {result.get_optimal_cost()}")
+
+# Plot the solution.
+plt.figure()
+plt.plot(np.cos(np.linspace(0, 2*np.pi, 100)), 2+np.sin(np.linspace(0, 2*np.pi, 100)))
+plt.plot(np.linspace(-2, 2, 100), np.power(np.linspace(-2, 2, 100), 2))
+plt.plot(p1_sol[0], p1_sol[1], '*')
+plt.plot(p2_sol[0], p2_sol[1], '*')
+plt.axis('equal')
+plt.show()

### 2023-12-05 plan_executor.py

@@ -37,7 +37,7 @@ def main():
 
     # Execute plan
     wait_for_user()
-    robot = Robot(world)
+    robot = Robot(world, use_trajopt=True)
     robot.move_base()
     for act in plan:
         print(act)

### 2023-12-05 robot.py

@@ -1,18 +1,24 @@
 import time
-from pybullet_tools.utils import set_joint_positions, set_pose, get_link_pose
+from pybullet_tools.utils import set_joint_positions, set_pose, get_link_pose, link_from_name
 from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
+from pybullet_tools.ikfast.ikfast import get_ik_joints
 from src.utils import rotate_robot, translate_linearly
 from constants import *
-from rrt import *
+from rrt import TrajectoryGenerator
+from trajopt import TrajectoryOptimizer
 
 class Robot:
 
-    def __init__(self, world):
+    def __init__(self, world, use_trajopt=False):
         self.world = world
         self.tool_link = link_from_name(world.robot, "panda_hand")
         self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
         self.sugar_box = self.world.get_body("sugar_box0")
         self.spam_box = self.world.get_body("potted_meat_can1")
+        if use_trajopt:
+            self.trajgen = TrajectoryOptimizer(world)
+        else:
+            self.trajgen = TrajectoryGenerator(world)
 
         self.function_map = {
             "open_storage":     {"drawer": self.open_drawer},
@@ -40,14 +46,14 @@ class Robot:
 
     def move_joint_init(self):
         time.sleep(ACTION_SLEEP)
-        path = TrajectoryGenerator().rrt(self.world, INIT_JOINT)
+        path = self.trajgen.solve(INIT_JOINT)
         for point in path:
             set_joint_positions(self.world.robot, self.ik_joints, point)
             time.sleep(JOINT_MOVE_SLEEP)
 
     def grab_sugar(self):
         time.sleep(ACTION_SLEEP)
-        path = TrajectoryGenerator().rrt(self.world, GRAB_SUGAR_JOINT)
+        path = self.trajgen.solve(GRAB_SUGAR_JOINT)
         for point in path:
             set_joint_positions(self.world.robot, self.ik_joints, point)
             time.sleep(JOINT_MOVE_SLEEP)
@@ -56,7 +62,7 @@ class Robot:
 
     def place_sugar(self):
         time.sleep(ACTION_SLEEP)
-        path = TrajectoryGenerator().rrt(self.world, PLACE_SUGAR_JOINT)
+        path = self.trajgen.solve(PLACE_SUGAR_JOINT)
[…]

### 2023-12-05 rrt.py

@@ -29,25 +29,27 @@ class Tree:
 
 class TrajectoryGenerator:
 
-    def rrt(self, world, goal_point):
-        tool_link = link_from_name(world.robot, 'panda_hand')
-        joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
-        sample_free = get_sample_fn(world.robot, world.arm_joints)
-        set_renderer(False)
+    def __init__(self, world):
+        self.world = world
+        self.tool_link = link_from_name(world.robot, 'panda_hand')
+        self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
+        self.sample_free = get_sample_fn(world.robot, world.arm_joints)
 
-        start_point = get_joint_positions(world.robot, world.arm_joints)
+    def solve(self, goal_point):
+        set_renderer(False)
+        start_point = get_joint_positions(self.world.robot, self.world.arm_joints)
         tree = Tree(start_point)
         count = 1
         while True:
-            rand_point = goal_point if count % GOAL_SAMPLE == 0 else sample_free() # Goal biasing
+            rand_point = goal_point if count % GOAL_SAMPLE == 0 else self.sample_free() # Goal biasing
             nearest = self.find_nearest(tree, rand_point)
             new_point = self.steer(nearest.point, rand_point)
-            if self.obstacle_free(world, joints, new_point):
+            if self.obstacle_free(new_point):
                 last_node = Tree(new_point)
                 nearest.add_child(last_node)
                 if math.dist(new_point, goal_point) <= GOAL_THRESHOLD: break # In goal state
             count += 1
-        set_joint_positions(world.robot, joints, start_point)
+        set_joint_positions(self.world.robot, self.ik_joints, start_point)
         set_renderer(True)
         return self.find_path(last_node)
 
@@ -60,9 +62,9 @@ class TrajectoryGenerator:
         if distance <= JOINT_STEP_SIZE: return rand_point
         return tuple((rand_point[i] - nearest_point[i]) * (JOINT_STEP_SIZE / distance) + nearest_point[i] for i in range(7))
 
-    def obstacle_free(self, world, joints, point):
-        set_joint_positions(world.robot, joints, point)
-        return not pairwise_collision(world.robot, world.kitchen)
+    def obstacle_free(self, point):
+        set_joint_positions(self.world.robot, self.ik_joints, point)
+        return not pairwise_collision(self.world.robot, self.world.kitchen)
 
     def find_path(self, goal):
         curr = goal

### 2023-12-05 test_drake.py

@@ -1,0 +1,63 @@
+import numpy as np
+import os
+import sys
+
+sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
+
+from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits
+from pydrake.all import MathematicalProgram, Solve
+from constants import *
+
+# Define the number of joints and the number of time steps
+num_joints = 7
+num_time_steps = 200  # You can adjust this based on your requirements
+
+# Create a MathematicalProgram
+prog = MathematicalProgram()
+
+# Create decision variables for joint positions, velocities, and time
+q_vars = prog.NewContinuousVariables(num_time_steps, num_joints, "q")
+time_var = prog.NewContinuousVariables(1, "time")[0]
+
+# Set initial and final joint positions
+q0 = np.array(INIT_JOINT)  # Initial joint positions
+qf = np.array(GRAB_SPAM_JOINT)  # Final joint positions
+
+# Set initial and final joint velocities
+qd0 = np.zeros(num_joints)
+qdf = np.zeros(num_joints)
+
+# Add constraints to ensure the initial and final joint positions and velocities
+for i in range(num_joints):
+    prog.AddConstraint(q_vars[0, :][i] == q0[i])
+    prog.AddConstraint(q_vars[-1, :][i] == qf[i])
+
+# Add a cost to minimize time
+prog.AddLinearCost(time_var)
+prog.AddLinearConstraint(time_var >= 1)
+
+# Add constraints to ensure the arm doesn't teleport
+for i in range(num_time_steps - 1):
+    for j in range(num_joints):
+        prog.AddConstraint((q_vars[i + 1, :][j] - q_vars[i, :][j]) / (time_var / num_time_steps) <= 0.01)
+        prog.AddConstraint((q_vars[i + 1, :][j] - q_vars[i, :][j]) / (time_var / num_time_steps) >= -0.01)
+
+lower = (-2.8973, -1.7628, -2.8973, -3.0718, -2.8973, -0.0175, -2.8973)
+upper = (2.8973, 1.7628, 2.8973, -0.0698, 2.8973, 3.7525, 2.8973)
+
+# Add joint constraints
+for i in range(num_time_steps):
+    for j in range(num_joints):
+        prog.AddConstraint(lower[j] <= q_vars[i, :][j])
+        prog.AddConstraint(q_vars[i, :][j] <= upper[j])
+
[…]

### 2023-12-05 test_example.py

@@ -15,6 +15,7 @@ from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinemati
 
 from src.world import World
 from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, ALL_JOINTS, compute_surface_aabb, rotate_robot, BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, add_ycb
+from trajopt import TrajectoryOptimizer
 from constants import *
 from rrt import *
 
@@ -72,16 +73,24 @@ def main():
         time.sleep(MOVE_SLEEP)
 
     """ THIRD CHUNK OF CODE: MOVING THE ROBOT ARM """
+
+    wait_for_user()
+    trajopt = TrajectoryOptimizer(world)
+    path = trajopt.solve()
+    for joint in path:
+        set_joint_positions(world.robot, ik_joints, joint)
+        time.sleep(JOINT_MOVE_SLEEP) 
+
 #
 #    wait_for_user()
-    print("Open drawer")
-    world.open_drawer()
+#    print("Open drawer")
+#    world.open_drawer()
 #
 
 #    print("Going to use IK to go from a sample start state to a goal state\n")
 #    wait_for_user()
-    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
-    start_pose = get_link_pose(world.robot, tool_link)
+#    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
+#    start_pose = get_link_pose(world.robot, tool_link)
 #    print("Start pose:", start_pose)
 #    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
 #    end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
@@ -91,11 +100,11 @@ def main():
 #    else:
 #        print(conf)
 #        set_joint_positions(world.robot, ik_joints, conf)
-
-    wait_for_user()
-    set_joint_positions(world.robot, ik_joints, STORE_SPAM_JOINT)
-    set_pose(world.get_body("potted_meat_can1"), MOVED_SPAM_POSE)
[…]

### 2023-12-05 trajopt.py

@@ -1,0 +1,83 @@
+import numpy as np
+import os
+import sys
+
+sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
+
+from pydrake.solvers import MathematicalProgram, Solve, Binding
+from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, interval_generator, get_joint_positions, set_renderer, set_joint_positions, pairwise_collision, get_link_pose
+from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
+from pybullet_tools.ikfast.ikfast import get_ik_joints
+from constants import *
+
+class TrajectoryOptimizer:
+
+    def __init__(self, world):
+        self.world = world
+        self.tool_link = link_from_name(world.robot, 'panda_hand')
+        self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
+
+    def solve(self, goal_joint):
+        set_renderer(False)
+        start_point = np.array(get_joint_positions(self.world.robot, self.world.arm_joints))
+
+        # Define the number of joints and the number of time steps
+        num_joints = 7
+
+        # Create a MathematicalProgram
+        prog = MathematicalProgram()
+
+        # Create decision variables for joint positions, velocities, and time
+        q_vars = prog.NewContinuousVariables(PATH_LENGTH, num_joints, "q")
+        time_var = prog.NewContinuousVariables(1, "time")[0]
+
+        # Set initial and final joint positions
+        q0 = start_point                    # Initial joint positions
+        qf = np.array(goal_joint)  # Final joint positions
+
+        # Add constraints to ensure the initial and final joint positions and velocities
+        for i in range(num_joints):
+            prog.AddConstraint(q_vars[0, :][i] == q0[i])
+            prog.AddConstraint(q_vars[-1, :][i] == qf[i])
+
+        # Add a cost to minimize time
+        prog.AddLinearCost(time_var)
+        prog.AddLinearConstraint(time_var >= 1)
+
+        # Add constraints to ensure the arm doesn't teleport
+        for i in range(PATH_LENGTH - 1):
+            for j in range(num_joints):
+                prog.AddConstraint((q_vars[i + 1, :][j] - q_vars[i, :][j]) / (time_var / PATH_LENGTH) <= 1)
[…]

### 2023-12-05 constants.py
add initial guess

@@ -3,8 +3,7 @@ import numpy as np
 # For animation purposes
 JOINT_MOVE_SLEEP = 0.04                    # Sleep time between joint movements
 ACTION_SLEEP     = 1                       # Sleep time between actions
-#MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
-MOVE_SLEEP       = 0                    # Sleep time for translation (for animation purposes)
+MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
 
 # Important constants
 SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box

### 2023-12-05 trajopt.py

@@ -17,7 +17,7 @@ class TrajectoryOptimizer:
         self.tool_link = link_from_name(world.robot, 'panda_hand')
         self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
 
-    def solve(self, goal_joint):
+    def solve(self, goal_point):
         set_renderer(False)
         start_point = np.array(get_joint_positions(self.world.robot, self.world.arm_joints))
 
@@ -31,9 +31,12 @@ class TrajectoryOptimizer:
         q_vars = prog.NewContinuousVariables(PATH_LENGTH, num_joints, "q")
         time_var = prog.NewContinuousVariables(1, "time")[0]
 
+        # Set the linspace as the initial guess
+        prog.SetInitialGuess(q_vars, np.linspace(start_point, goal_point, PATH_LENGTH))
+
         # Set initial and final joint positions
         q0 = start_point                    # Initial joint positions
-        qf = np.array(goal_joint)  # Final joint positions
+        qf = np.array(goal_point)  # Final joint positions
 
         # Add constraints to ensure the initial and final joint positions and velocities
         for i in range(num_joints):

### 2023-12-07 constants.py
finished part 3

@@ -6,12 +6,13 @@ ACTION_SLEEP     = 1                       # Sleep time between actions
 MOVE_SLEEP       = 0.03                    # Sleep time for translation (for animation purposes)
 
 # Important constants
+NUM_JOINTS       = 7                       # Robot has 7 joints
 SUGAR_BOX_POSE   = (-0.1, 0.65, np.pi / 4) # Starting position of sugar box
 SPAM_BOX_POSE    = (0.2, 1.1, np.pi / 4)   # Starting position of spam box
 JOINT_STEP_SIZE  = 0.02                    # Step size of robot arm interpolation and RRT
 GOAL_SAMPLE      = 50                      # Sample goal every X times
 GOAL_THRESHOLD   = 0.15                    # If distance less than this, then it is in goal state
-PATH_LENGTH  = 200                         # Path length for constraint optimization solver
+PATH_LENGTH      = 200                         # Path length for constraint optimization solver
 
 # Pose of objects after being moved
 MOVED_SUGAR_POSE = (0.1, 1.0, -0.6),  (0, 0, 0, 1) 
@@ -23,6 +24,7 @@ INIT_JOINT          = (0.01200158428400755, -0.5697816014289856, 5.6801487517077
 GRAB_SUGAR_JOINT    = (-0.10029298683257405, 0.8075911195804472, 0.06859836909844828, -1.4332957958078696, 0.019711396650709645, 3.024185878659845, 0.6934382572596789)
 PLACE_SUGAR_JOINT   = (-0.8333839072116455, 0.8531772629931089, 0.4617390279322891, -1.381649993484035, 0.30737591885150817, 2.8317178374508676, -0.11349712635040898)
 GRAB_SPAM_JOINT     = (-0.2952415992141341, 0.7212760573498352, -0.5825837608323721, -1.9038112672075966, 2.43044497001763, 1.7815317165161315, -1.6864013281698946)
+DRAWER_CLOSED_INTERMEDIATE = (0.9511187775262453, -1.7396685466779997, -1.4872401065919303, -1.860683910611634, -0.4777817191196396, 2.7740711389454673, 1.1463138823909778)
 DRAWER_CLOSED_JOINT = (-1.338462590924967, 1.0771823871221202, 0.18560027115857658, -1.5159392166440764, 1.7676538992294342, 1.87285428791979, -0.2862073274847683)
[…]

### 2023-12-07 robot.py

@@ -1,4 +1,5 @@
 import time
+import numpy as np
 from pybullet_tools.utils import set_joint_positions, set_pose, get_link_pose, link_from_name
 from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
 from pybullet_tools.ikfast.ikfast import get_ik_joints
@@ -15,6 +16,7 @@ class Robot:
         self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
         self.sugar_box = self.world.get_body("sugar_box0")
         self.spam_box = self.world.get_body("potted_meat_can1")
+        self.use_trajopt = use_trajopt
         if use_trajopt:
             self.trajgen = TrajectoryOptimizer(world)
         else:
@@ -28,6 +30,14 @@ class Robot:
             "place_openable":   {"sugar":  self.place_sugar, "spam": self.place_spam},
             "place_static":     {"sugar":  self.place_sugar, "spam": self.place_spam},
         }
+
+    def get_init_guess(self, filename):
+        data = np.load(filename)
+        datasize = data.shape[0]
+        interp_data = np.zeros((PATH_LENGTH, NUM_JOINTS))
+        for i in range(NUM_JOINTS):
+            interp_data[:, i] = np.interp(np.linspace(0, datasize - 1, PATH_LENGTH), np.arange(0, datasize), data[:, i])
+        return interp_data
 
     def move_base(self):
         for _ in range(45):
@@ -53,7 +63,7 @@ class Robot:
 
     def grab_sugar(self):
         time.sleep(ACTION_SLEEP)
-        path = self.trajgen.solve(GRAB_SUGAR_JOINT)
+        path = self.trajgen.solve(GRAB_SUGAR_JOINT, self.get_init_guess("npy/to_sugar.npy"))
         for point in path:
             set_joint_positions(self.world.robot, self.ik_joints, point)
             time.sleep(JOINT_MOVE_SLEEP)
@@ -62,7 +72,7 @@ class Robot:
 
     def place_sugar(self):
         time.sleep(ACTION_SLEEP)
-        path = self.trajgen.solve(PLACE_SUGAR_JOINT)
+        path = self.trajgen.solve(PLACE_SUGAR_JOINT, self.get_init_guess("npy/place_sugar.npy"))
         for point in path:
             set_pose(self.sugar_box, get_link_pose(self.world.robot, self.tool_link))
[…]

### 2023-12-07 rrt.py

@@ -35,7 +35,7 @@ class TrajectoryGenerator:
         self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
         self.sample_free = get_sample_fn(world.robot, world.arm_joints)
 
-    def solve(self, goal_point):
+    def solve(self, goal_point, *args):
         set_renderer(False)
         start_point = get_joint_positions(self.world.robot, self.world.arm_joints)
         tree = Tree(start_point)

### 2023-12-07 test_example.py

@@ -74,12 +74,12 @@ def main():
 
     """ THIRD CHUNK OF CODE: MOVING THE ROBOT ARM """
 
-    wait_for_user()
-    trajopt = TrajectoryOptimizer(world)
-    path = trajopt.solve()
-    for joint in path:
-        set_joint_positions(world.robot, ik_joints, joint)
-        time.sleep(JOINT_MOVE_SLEEP) 
+#    wait_for_user()
+#    trajopt = TrajectoryOptimizer(world)
+#    path = trajopt.solve(DRAWER_CLOSED_JOINT)
+#    for joint in path:
+#        set_joint_positions(world.robot, ik_joints, joint)
+#        time.sleep(JOINT_MOVE_SLEEP) 
 
 #
 #    wait_for_user()
@@ -87,19 +87,20 @@ def main():
 #    world.open_drawer()
 #
 
-#    print("Going to use IK to go from a sample start state to a goal state\n")
-#    wait_for_user()
-#    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
-#    start_pose = get_link_pose(world.robot, tool_link)
-#    print("Start pose:", start_pose)
-#    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
-#    end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
-#    conf = next(closest_inverse_kinematics(world.robot, PANDA_INFO, tool_link, end_pose, max_time=0.05), None)
-#    if conf is None:
-#        print('Failure!')
-#    else:
-#        print(conf)
-#        set_joint_positions(world.robot, ik_joints, conf)
+    print("Going to use IK to go from a sample start state to a goal state\n")
+    wait_for_user()
+    ik_joints = get_ik_joints(world.robot, PANDA_INFO, tool_link)
+    start_pose = get_link_pose(world.robot, tool_link)
+    print("Start pose:", start_pose)
+    #end_pose = (0.45, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer closed
+    #end_pose = (0.75, 1.2, -0.65), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
+    end_pose = (0.45, 1.2, -0.35), (-0.5, -0.5, 0.5, 0.5) # Drawer opened
[…]

### 2023-12-07 trajopt.py

@@ -4,8 +4,8 @@ import sys
 
 sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
-from pydrake.solvers import MathematicalProgram, Solve, Binding
-from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, interval_generator, get_joint_positions, set_renderer, set_joint_positions, pairwise_collision, get_link_pose
+from pydrake.solvers import MathematicalProgram, Solve
+from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, get_joint_positions, set_joint_positions, pairwise_collision
 from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
 from pybullet_tools.ikfast.ikfast import get_ik_joints
 from constants import *
@@ -17,59 +17,61 @@ class TrajectoryOptimizer:
         self.tool_link = link_from_name(world.robot, 'panda_hand')
         self.ik_joints = get_ik_joints(world.robot, PANDA_INFO, self.tool_link)
 
-    def solve(self, goal_point):
-        set_renderer(False)
+    def solve(self, goal_point, init_guess=None):
         start_point = np.array(get_joint_positions(self.world.robot, self.world.arm_joints))
 
         # Define the number of joints and the number of time steps
-        num_joints = 7
+        NUM_JOINTS = 7
 
         # Create a MathematicalProgram
         prog = MathematicalProgram()
 
         # Create decision variables for joint positions, velocities, and time
-        q_vars = prog.NewContinuousVariables(PATH_LENGTH, num_joints, "q")
+        q_vars = prog.NewContinuousVariables(PATH_LENGTH, NUM_JOINTS, "q")
         time_var = prog.NewContinuousVariables(1, "time")[0]
 
-        # Set the linspace as the initial guess
-        prog.SetInitialGuess(q_vars, np.linspace(start_point, goal_point, PATH_LENGTH))
+        # Set initial guess
+        if init_guess is not None:
+            prog.SetInitialGuess(q_vars, init_guess)
 
         # Set initial and final joint positions
-        q0 = start_point                    # Initial joint positions
-        qf = np.array(goal_point)  # Final joint positions
+        q0 = start_point
+        qf = np.array(goal_point)
 
[…]

### 2023-12-09 paper/main.tex
initial trajopt complete
yayayay im done

@@
 Activity planing, motion planning, and trajectory optimization for a robotic arm is challenging.
-To navigate around an environment, the agent must perform a state space search to plan a sequence of actions and generate a trajectory by either using a sample based planner or modeling the problem as a constraint optimization problem.
+To navigate around an environment, the agent must perform a state space search to plan a sequence of actions and generate a trajectory by using a sample-based planner or modeling the problem as an optimization problem.
 This project explores 1) defining an activity planning problem with the Planning Domain Definition Language, 2) implementing the Fast-Forward heuristic planner with Enforced Hill Climbing, 3) using RRT with goal-biasing for trajectory generation, and 4) comparing the results with the trajectory generated by constraint optimization.
@@
 
-\iffalse
-\subsection{Problem Statement}
-
-The simulator consists of a kitchen environment with drawers, cabinets, countertops, and a robot manipulator arm.
-In addition, sugar and spam boxes are placed on a stovetop burner and a countertop.
-The objective is to move the sugar box to a nearby countertop and store the spam box inside the red drawer below it.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=200px]{sim_env.jpg}
-    \caption{The kitchen simulation environment.}
-    \label{fig:sim_env}
-\end{figure}
-\fi
-
 \subsection{PDDL Domain and Problem}
@@
 The PDDL domain and problem files encode the problem as sets of objects, types, predicates, actions, and goals.
-There are two main types of objects: the \texttt{box} type and the \texttt{storage} type.
-The \texttt{box} type represents the sugar and spam boxes which are manipulated by the robot arm, and the \texttt{storage} type represents the storage spaces in the kitchen.
-In addition, I separated the \texttt{storage} type into two subtypes: \texttt{static}, which are storage spaces without actions (stovetop burner and countertop), and \texttt{openable}, which are storage spaces that can be opened or closed (drawer, cabinet).
+There are two main types of objects: the \texttt{box} type, which represents the sugar/spam boxes that are manipulated by the robot arm, and the \texttt{storage} type, which represents the storage spaces in the kitchen.
+In addition, the \texttt{storage} type is separated into two subtypes: \texttt{static}, which are storage spaces without actions (stovetop burner and countertop), and \texttt{openable}, which are storage spaces that can be opened or closed (drawer, cabinet).
 
@@
 Because we defined our actions to only have positive preconditions, we can easily determine whether an action is applicable by checking if the precondition is a subset of \texttt{new\_state}.
-$h_{ff}$ is an admissible heuristic that always underestimates the number of actions it takes to reach the goal state, hence an alternative algorithm such as A* could have been used to find the optimal path.
 
 In this project, I decided to implement Enforced Hill Climbing in the \texttt{solve\_ff} function.
-While EHC is not guaranteed to find the optimal solution, its greedy nature typically leads to higher efficiency and lower memory usage.
+While EHC is not guaranteed to find an optimal solution, its greedy nature typically leads to higher efficiency and lower memory usage.
 \texttt{solve\_ff} initially parses the PDDL files and enumerates all possible actions that can be taken by the agent.
-Next, it performs a greedy search by immediately adding an action that leads to a strictly smaller $h_{ff}$ to the plan.
+Next, it performs a greedy search by adding the first action that leads to a strictly smaller $h_{ff}$ to the plan.
 If no such action is found, there is a ``plateau" in the graph, and BFS is used to find a sequence of actions that lead to a smaller $h_{ff}$.
-If BFS fails to find such action, then the algorithm determines that the activity planning problem is unsolvable.
+If BFS fails to find such sequence of actions, then the algorithm determines that the activity planning problem is unsolvable.
 
@@
 $950\mu s$).
-This is most likely because the plan graph is rather simple for this problem.
+This is because the plan graph is rather simple for this problem.
 For example, the starting state has $h_{ff}=2$, meaning EHC gets stuck on a ``plateau" for most of the time, resorting to BFS.
-In this case, calculating $h_{ff}$ leads to extra computation time.
+In this case, calculating $h_{ff}$ leads to computational overhead.
 For more complex problems requiring many actions to be taken, I expect the FF Heuristic Planner to perform significantly faster than BFS.
@@
 
-In addition, the following assumptions were made when implementing the motion planner:
+In addition, the following environment assumptions were made:
 \begin{itemize}
@@
 \texttt{get\_sample\_fn} returns a sampling function that returns a random valid joint configuration $x_\text{rand}$.
-I also defined a class \texttt{Tree} which keeps track of its \texttt{parent}, \texttt{children}, and value (\texttt{point}), which is the 7D joint configuration.
-\texttt{Tree} has function \texttt{add\_child}, which appends a new \texttt{Tree} to its \texttt{children} and sets the child's \texttt{parent} to itself.
+I also defined a class \texttt{Tree} which keeps track of its \texttt{parent}, \texttt{children}, and \texttt{point} (joint configuration), and has a method \texttt{add\_child} which appends a new \texttt{Tree} to its \texttt{children} and sets the child's \texttt{parent} to itself.
 
-Class \texttt{TrajectoryGenerator} contains the main motion planning algorithm in the \texttt{rrt} method. It also includes four helper functions:
+Class \texttt{TrajectoryGenerator} contains the main motion planning algorithm in the \texttt{solve} method. It also includes four helper functions:
 \begin{enumerate}
     \item \texttt{find\_nearest}: returns $x_\text{nearest}$, the node in the tree closest to $x_\text{rand}$ by recursively traversing the tree.
-    \item \texttt{steer}: creates a straight line from $x_\text{nearest}$ to $x_\text{rand}$ limited to length \texttt{JOINT\_STEP\_SIZE}. Returns this new point $x_\text{new}$.
+    \item \texttt{steer}: creates a line from $x_\text{nearest}$ to $x_\text{rand}$ limited to length \texttt{JOINT\_STEP\_SIZE}. Returns this new point $x_\text{new}$.
     \item \texttt{obstacle\_free}: returns true if the input joint configuration does not cause the robot to collide with a kitchen object.
@@
 
-Instead of getting a random sample every time, the algorithm uses the goal state as the ``random" value every \texttt{GOAL\_SAMPLE} cycles to bias the tree towards the goal.
+Instead of getting a random sample every time, the algorithm samples the goal state every \texttt{GOAL\_SAMPLE} cycles to bias the tree.
 Additionally, we determine whether $x_\text{new}$ is in the goal state by checking if the euclidian distance between $x_\text{new}$ and $x_\text{goal}$ is less than \texttt{GOAL\_THRESHOLD}.
@@
 
-The \texttt{robot.py} file includes a \texttt{Robot} class with methods for each action in the PDDL domain.
-It also includes methods to move the robot base closer to the objects and the robot arm back to the initial state.
-Finally, the dictionary \texttt{function\_map} maps PDDL actions to its corresponding methods, and the \texttt{act} method uses this dictionary to perform a task based on the input PDDL action.
+The \texttt{robot.py} file includes a \texttt{Robot} class with methods for each action in the PDDL domain in addition to methods to move the robot base and arm to the initial state.
+Dictionary \texttt{function\_map} maps PDDL actions to its corresponding methods, and the \texttt{act} method uses \texttt{function\_map} to perform a task based on a given action.
 
@@
 
+To view the trajectory optimization in action, see \href{https://drive.google.com/file/d/1ZB1DUmpl6Mqf19IPNjAWVvW_RhoJtXB6/view?usp=sharing}{Trajectory optimization} or go to the following url: \url{https://drive.google.com/file/d/1ZB1DUmpl6Mqf19IPNjAWVvW_RhoJtXB6/view?usp=sharing}.
+
+\subsection{File organization}
+
+Trajectory optimization is implemented in pydrake using the default IPOPT nonlinear optimization solver, and can be found in \texttt{trajopt.py}.
+The \texttt{solve} function in the \texttt{TrajectoryOptimizer} class solves the optimization problem defined in \href{sec:opt}{Optimization problem definition} and takes an initial guess of the arm trajectory as an optional argument to seed the solver.
+Furthermore, the \texttt{Robot} class constructor has an additional \texttt{use\_trajopt} argument which allows the use of \texttt{TrajectoryOptimizer} to generate the arm trajectory.
+Finally, the trajectories generated from the sample-based motion planner were saved as \texttt{.npy} files in the \texttt{npy} folder.
+To use these trajectories as inputs to the IPOPT solver, I added a new \texttt{Robot().get\_init\_guess} method which loads a \texttt{.npy} file and linearly interpolates \texttt{PATH\_LENGTH} sample points.
+The solver generates a trajectory encoded as a $\mathtt{PATH\_LENGTH}\times7$ matrix, so the initial guess must also be of the same size.
+
+\subsection{Optimization problem definition}
+\label{sec:opt}
+
+The kinematic trajectory optimization formulation is inspired from the problem used in Professor Russ Tedrake's Robotic Manipulation course \cite{Tedrake}:
+
+\begin{equation*}
+\begin{aligned}
+    \min_T\quad & T,\\
+    \textrm{subject to}\quad & X^{G_{start}}=f_{kin}(q(0)),\\
+                             & X^{G_{goal}}=f_{kin}(q(T)),\\
+                             & \forall t,\quad |\dot q|\le v_{max},
+\end{aligned}
+\end{equation*}
+
+Where $f_{kin}$ is the forward kinematics function and $q(t)$ is the joint state of the robot at time $t$.
+The problem reads as minimizing time $T$ for the arm to move from the start pose $X^{G_{start}}$ to the goal pose $X^{G_{goal}}$ while satisfying velocity constraints.
+
+There are a few challenges when converting this problem into a pydrake \texttt{MathematicalProgram}.
+Since pydrake does not allow pybullet functions to be included in its problem formulation, I simplified the problem to input initial and goal joint states rather than poses, and did not encode collision detection.
+Moreover, pydrake does not allow indexing into a variable using another variable.
+To avoid this problem, I hard-coded the length of the arm trajectory to be $\mathtt{PATH\_LENGTH}=200$ defined in \texttt{constants.py}.
+Finally, I approximated the joint velocities as the following: $\dot q\approx \frac{q(t+1)-q(t)}{T/\texttt{PATH\_LENGTH}}\quad\forall t\in\{0,\dots,T-1\}$.
+Bringing it all together, the new optimization problem is the following:
+
+\begin{equation*}
+\begin{aligned}
+    \min_T\quad & T,\\
+    \textrm{subject to}\quad & q_0=q[0],\\
+                             & q_f=q[T],\\
+                             & \forall t\in\{0,\dots,T-1\},\quad \frac{q[t+1]-q[t]}{T/\texttt{PATH\_LENGTH}}\le v_{max},\\
+                             & \forall t\in\{0,\dots,T-1\},\quad \frac{q[t+1]-q[t]}{T/\texttt{PATH\_LENGTH}}\ge -v_{max}
+\end{aligned}
+\end{equation*}
+
+where $q_0$ is the initial joint state and $q_f$ is the goal joint state.
+When running the program, the generated trajectories were smooth but inefficient as the solver found solutions with nonoptimal local minima.
+While this was alleviated by seeding the solver with initial guesses, it caused the optimized trajectories to be jagged since the given RRT trajectories exhibited a ``shaking" motion.
+To prevent such trajectories, I added another set of constraints to limit the acceleration of the joints:
+
+\begin{equation*}
+\begin{aligned}
+    \forall t\in\{0,\dots,T-2\},\quad \frac{(q[t+2]-q[t+1])-(q[t+1]-q[t])}{2T/\texttt{PATH\_LENGTH}}\le a_{max},\\
+    \forall t\in\{0,\dots,T-2\},\quad \frac{(q[t+2]-q[t+1])-(q[t+1]-q[t])}{2T/\texttt{PATH\_LENGTH}}\ge -a_{max}
+\end{aligned}
+\end{equation*}
+
+Compared to the sample-based motion planner, the end result was smoother and more controlled trajectories but slower computation due to the greater number of constraints.
+Although some actions continued to cause the arm to move inefficiently, this is because the chioces of the goal joints can be improved.
+Implementing a custom forward kinematics function compatible with pydrake and setting the goal state as $X^{G_{goal}}=f_{kin}(q(T))$ will allow the program to find more optimal trajectories.
+Finally, to implement collision avoidance, I would encode the kitchen environment in pydrake and prevent the end-effector from colliding with the environment.
+However, I expect adding these two sets of constraints to significantly slow down computation.
+
 \section{Conclusion}
 
-%%% TODO: EDIT REFERENCES %%%
-\cite{Cui1}
+Using PDDL and the Fast-Forward heuristic planner is an efficient way to encode and solve an activity planning problem.
+Although the benefits of using the FF heuristic was unclear in this paper, it can improve performance when solving more complicated problems without many heuristic ``plateaus".
+Both the sample-based motion planner and nonlinear constraint optimization are valid ways to execute the generated plan.
+However, constraint optimization, with its ability to precisely encode robot dynamics, yielded a smoother and more optimized trajectory compared to the RRT implementation.
+Using complex algorithms such as RRT* may result in finding an optimal trajectory, but the required computation power may be too high.
+Similarly, adding more constraints to encode collision avoidance will result in slower computation for the nonlinear optimizer.
+For both activity and motion planning, it is essential to consider the compromise between runtime and finding a near-optimal solution, and choose the solution that benefits the program the most.
 

### 2023-12-09 constants.py

@@ -24,7 +24,6 @@ INIT_JOINT          = (0.01200158428400755, -0.5697816014289856, 5.6801487517077
 GRAB_SUGAR_JOINT    = (-0.10029298683257405, 0.8075911195804472, 0.06859836909844828, -1.4332957958078696, 0.019711396650709645, 3.024185878659845, 0.6934382572596789)
 PLACE_SUGAR_JOINT   = (-0.8333839072116455, 0.8531772629931089, 0.4617390279322891, -1.381649993484035, 0.30737591885150817, 2.8317178374508676, -0.11349712635040898)
 GRAB_SPAM_JOINT     = (-0.2952415992141341, 0.7212760573498352, -0.5825837608323721, -1.9038112672075966, 2.43044497001763, 1.7815317165161315, -1.6864013281698946)
-DRAWER_CLOSED_INTERMEDIATE = (0.9511187775262453, -1.7396685466779997, -1.4872401065919303, -1.860683910611634, -0.4777817191196396, 2.7740711389454673, 1.1463138823909778)
 DRAWER_CLOSED_JOINT = (-1.338462590924967, 1.0771823871221202, 0.18560027115857658, -1.5159392166440764, 1.7676538992294342, 1.87285428791979, -0.2862073274847683)
 DRAWER_OPEN_JOINT   = (-1.8639326887555299, 0.9974156273734971, 0.16949275359024293, -1.685524605166771, 1.32792178177285, 1.6055275415848749, -0.30157951704149566)
 STORE_SPAM_JOINT    = (0.8141463627352259, -1.7561537326062215, -1.7082003565419186, -1.9041165022131183, -0.06483606045010992, 2.7332450779369095, -0.954724282200727)

### 2023-12-09 example_drake.py

@@ -1,47 +1,0 @@
-from pydrake.solvers import MathematicalProgram, Solve
-import numpy as np
-import matplotlib.pyplot as plt
-
-prog = MathematicalProgram()
-p1 = prog.NewContinuousVariables(2, "p1")
-p2 = prog.NewContinuousVariables(2, "p2")
-
-# Add the constraint that p1 is on the unit circle centered at (0, 2)
-prog.AddConstraint(
-    lambda z: [z[0]**2 + (z[1]-2)**2],
-    lb=np.array([1.]),
-    ub=np.array([1.]),
-    vars=p1)
-
-# Add the constraint that p2 is on the curve y=x*x
-prog.AddConstraint(
-    lambda z: [z[1] - z[0]**2],
-    lb=[0.],
-    ub=[0.],
-    vars=p2)
-
-# Add the cost on the distance between p1 and p2
-prog.AddQuadraticCost((p1-p2).dot(p1-p2))
-
-# Set the value of p1 in initial guess to be [0, 1]
-prog.SetInitialGuess(p1, [0., 1.])
-# Set the value of p2 in initial guess to be [1, 1]
-prog.SetInitialGuess(p2, [1., 1.])
-
-# Now solve the program
-result = Solve(prog)
-print(f"Is optimization successful? {result.is_success()}")
-p1_sol = result.GetSolution(p1)
-p2_sol = result.GetSolution(p2)
-print(f"solution to p1 {p1_sol}")
-print(f"solution to p2 {p2_sol}")
-print(f"optimal cost {result.get_optimal_cost()}")
-
-# Plot the solution.
-plt.figure()
-plt.plot(np.cos(np.linspace(0, 2*np.pi, 100)), 2+np.sin(np.linspace(0, 2*np.pi, 100)))
-plt.plot(np.linspace(-2, 2, 100), np.power(np.linspace(-2, 2, 100), 2))
-plt.plot(p1_sol[0], p1_sol[1], '*')
-plt.plot(p2_sol[0], p2_sol[1], '*')
-plt.axis('equal')
-plt.show()

### 2023-12-09 test_drake.py

@@ -1,63 +1,0 @@
-import numpy as np
-import os
-import sys
-
-sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
-
-from pybullet_tools.utils import CIRCULAR_LIMITS, get_custom_limits
-from pydrake.all import MathematicalProgram, Solve
-from constants import *
-
-# Define the number of joints and the number of time steps
-num_joints = 7
-num_time_steps = 200  # You can adjust this based on your requirements
-
-# Create a MathematicalProgram
-prog = MathematicalProgram()
-
-# Create decision variables for joint positions, velocities, and time
-q_vars = prog.NewContinuousVariables(num_time_steps, num_joints, "q")
-time_var = prog.NewContinuousVariables(1, "time")[0]
-
-# Set initial and final joint positions
-q0 = np.array(INIT_JOINT)  # Initial joint positions
-qf = np.array(GRAB_SPAM_JOINT)  # Final joint positions
-
-# Set initial and final joint velocities
-qd0 = np.zeros(num_joints)
-qdf = np.zeros(num_joints)
-
-# Add constraints to ensure the initial and final joint positions and velocities
-for i in range(num_joints):
-    prog.AddConstraint(q_vars[0, :][i] == q0[i])
-    prog.AddConstraint(q_vars[-1, :][i] == qf[i])
-
-# Add a cost to minimize time
-prog.AddLinearCost(time_var)
-prog.AddLinearConstraint(time_var >= 1)
-
-# Add constraints to ensure the arm doesn't teleport
-for i in range(num_time_steps - 1):
-    for j in range(num_joints):
-        prog.AddConstraint((q_vars[i + 1, :][j] - q_vars[i, :][j]) / (time_var / num_time_steps) <= 0.01)
-        prog.AddConstraint((q_vars[i + 1, :][j] - q_vars[i, :][j]) / (time_var / num_time_steps) >= -0.01)
-
-lower = (-2.8973, -1.7628, -2.8973, -3.0718, -2.8973, -0.0175, -2.8973)
-upper = (2.8973, 1.7628, 2.8973, -0.0698, 2.8973, 3.7525, 2.8973)
-
-# Add joint constraints
-for i in range(num_time_steps):
-    for j in range(num_joints):
-        prog.AddConstraint(lower[j] <= q_vars[i, :][j])
-        prog.AddConstraint(q_vars[i, :][j] <= upper[j])
-
[…]

### 2023-12-09 test_example.py

@@ -1,199 +1,0 @@
-from __future__ import print_function
-
-import os
-import sys
-import argparse
-import time
-import numpy as np
-
-sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
-
-from pybullet_tools.utils import set_pose, Pose, Point, Euler, multiply, get_pose, get_point, create_box, set_all_static, WorldSaver, create_plane, COLOR_FROM_NAME, stable_z_on_aabb, pairwise_collision, single_collision, elapsed_time, get_aabb_extent, get_aabb, create_cylinder, set_point, get_function_name, wait_for_user, dump_world, set_random_seed, set_numpy_seed, get_random_seed, get_numpy_seed, link_from_name, get_movable_joints, get_joint_name, CIRCULAR_LIMITS, get_custom_limits, set_joint_positions, get_joint_positions, interval_generator, get_link_pose, interpolate_poses, set_renderer
-
-from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO, FRANKA_URDF
-from pybullet_tools.ikfast.ikfast import get_ik_joints, closest_inverse_kinematics
-
-from src.world import World
-from src.utils import JOINT_TEMPLATE, BLOCK_SIZES, BLOCK_COLORS, COUNTERS, ALL_JOINTS, compute_surface_aabb, rotate_robot, BLOCK_TEMPLATE, name_from_type, GRASP_TYPES, SIDE_GRASP, joint_from_name, STOVES, TOP_GRASP, randomize, LEFT_DOOR, point_from_pose, translate_linearly, add_ycb
-from trajopt import TrajectoryOptimizer
-from constants import *
-from rrt import *
-
-add_sugar_box = lambda world, **kwargs: add_ycb(world, 'sugar_box', **kwargs)
-add_spam_box = lambda world, **kwargs: add_ycb(world, 'potted_meat_can', **kwargs)
-
-""" MAIN CODE """
-
-def main():
-
-    """ FIRST CHUNK OF CODE: WORLD SETUP """
-
-    print('Random seed:', get_random_seed())
-    print('Numpy seed:', get_numpy_seed())
-
-    np.set_printoptions(precision=3, suppress=True)
-    world = World(use_gui=True)
-    sugar_box = add_sugar_box(world, idx=0, counter=1, pose2d=SUGAR_BOX_POSE)
[…]

### 2023-12-09 trajopt.py

@@ -5,7 +5,7 @@ import sys
 sys.path.extend(os.path.abspath(os.path.join(os.getcwd(), d)) for d in ['pddlstream', 'ss-pybullet'])
 
 from pydrake.solvers import MathematicalProgram, Solve
-from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, get_joint_positions, set_joint_positions, pairwise_collision
+from pybullet_tools.utils import CIRCULAR_LIMITS, link_from_name, get_custom_limits, get_joint_positions
 from pybullet_tools.ikfast.franka_panda.ik import PANDA_INFO
 from pybullet_tools.ikfast.ikfast import get_ik_joints
 from constants import *
@@ -19,9 +19,6 @@ class TrajectoryOptimizer:
 
     def solve(self, goal_point, init_guess=None):
         start_point = np.array(get_joint_positions(self.world.robot, self.world.arm_joints))
-
-        # Define the number of joints and the number of time steps
-        NUM_JOINTS = 7
 
         # Create a MathematicalProgram
         prog = MathematicalProgram()
@@ -74,10 +71,3 @@ class TrajectoryOptimizer:
         q_opt = result.GetSolution(q_vars)
 
         return q_opt
-
-    def obstacle_free(self, q):
-        point = []
-        for val in q:
-            point.append(val.value())
-        set_joint_positions(self.world.robot, self.ik_joints, point)
-        return not pairwise_collision(self.world.robot, self.world.kitchen)
